Learning and comparing functional connectomes between populations

### 2012-12-27 paper.tex
iter

Mutual information? Entropy correlation? MI as measure of integration (Marralec)

Small world networks, transport properties, resilient...
\cite{achard2006,bullmore2009}

>>>>

\paragraph{Network integration}
%
To avoid the multiple comparison issue and to capture the network-level
distributed variability, a possible strategy is to perform comparison and
statistical testing at the level of the network, rather than the
individual connection. In particular, Marrelec \emph{et al.}\
\cite{marrelec2008} introduce the use of entropy and mutual information
as a measure of network integration\footnote{See \cite{varoquaux2010c}
for simplified formulas for network integration and mutual information.}.
Gaussian entropy can be seen as a simple metric to generalize correlation
or variance to multiple nodes (see \cite{anderson1958} \S2.5.2 and
\S7.5). Indeed, let us considering 3 nodes: $a$, $b$ and $c$. Their
correlation structure is captured by three correlation coefficients:
$\rho_{ab}$, $\rho_{bc}$ and $\rho_{ac}$.

% Rmk average of correlations will measure the sphericity of the
% distribution

%{{{------ Integration measure -----------------------------------------------
\begin{figure}
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    1.513
\end{minipage}%
\begin{minipage}{.25\linewidth}
    \includegraphics[width=\linewidth]{correlation_ex1.pdf}
\end{minipage}%
\hfill%
\begin{minipage}{.25\linewidth}
    \includegraphics[width=\linewidth]{correlation_ex2.pdf}
\end{minipage}%
\begin{minipage}{.19\linewidth}
    \center\sffamily
    {\small Integration:}

    0.492
\end{minipage}%

\caption{Two different correlation matrix with the same average
correlation, but integration values that strongly differ.
\label{fig:integration}}
\end{figure}
%---------------------------------------------------------------------------}}}

\paragraph{Graph-topology metrics}
%
Small world networks, transport properties, resilient...
\cite{achard2006,bullmore2009}
